Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-09-17 Ben_Manuscripts/structure_paper/Draft.tex
Converting to pdfs

%MRS5: could be punchier. I will keep thinking.  
\title{Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
\author{Benjamin J. Coscia}
\author{Joe Yelk}
\author{Matthew A. Glaser}
\affiliation{Department of Physics, University of Colorado Boulder, Boulder CO, 80309, USA}
\author{Richard D. Noble}
\author{Douglas L. Gin}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\alsoaffiliation{Department of Chemistry and Biochemistry, University of Colorado Boulder, Boulder CO 80309, USA}
\author{Xunda Feng}
\affiliation{Department of Chemical and Environmental Engineering, Yale University, New Haven, Connecticut 06511, USA}
\author{Michael R. Shirts}
\email{michael.shirts@colorado.edu}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\begin{document}
%MRS13: we might end up adjusting the author list a bit; I will ask Matt where he thinks he and Joe should go.  I will talk to Rich when we get this going; not clear that he actually has contributed.  But that's my job. 
  \graphicspath{{./figures/}}

@@

  \begin{figure}
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{NaGA3C11.eps}
		\caption{}~\label{fig:monomer}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{monomer_twocolor.png}
		\caption{}~\label{fig:atomistic_monomer}
	\end{subfigure}
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{wedge_thick.png}
		\caption{}~\label{fig:wedge}
	\end{subfigure}
		\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{columns.png}
		\caption{}~\label{fig:wedge_layer}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{hexagonal_packing.png}
		\caption{}~\label{fig:hex_packing_simple}
	\end{subfigure}
	\caption{(a) The LLC monomer Na-GA3C11 (b) rendered atomistically (c)
	exhibits wedge-like character. (d) Monomers stack on top of each other to
	create columns with short range order then assemble into pores with  
	hydrophilic head groups (blue) face towards the pore center. (e) The 
	pores assemble into hexagonally packed columnar mesophases.}~\label{fig:assembly}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{cartoon_pore.png}
		\caption{}~\label{fig:undetailed_pore}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{detailed_pore.png}
		\caption{}~\label{fig:detailed_pore}
	\end{subfigure}
    \caption{(a) Previous understanding of the pores are essentially speculations 
    based on limited chemical and experimental data. (b) We use detailed molecular 
    modeling in this paper in order to appropriately model the pore's complex architecture
    which is crucial to understanding the mechanism of solute transport. In both 
    pictures, the head group region is colored blue and the tail region is colored cyan.}~\label{fig:detail}
  \end{figure}

@@

  \begin{figure}[!htb]
        \centering
                \begin{subfigure}[t]{0.495\linewidth}
                \centering
                \includegraphics[width=\linewidth]{WAXS_annotated_words.png} 
                \caption{}\label{fig:WAXS}
        \end{subfigure}
	\begin{subfigure}[t]{0.405\linewidth}
                \centering
                \includegraphics[width=\linewidth]{SAXS.png}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
	\caption{(a) 2D WAXS gives details about repeating features on the
		order of angstroms. Experimentalists have explained each of the 5 major
		reflections present as follows: (R-$\pi$) Aromatic head groups $\pi-\pi$ stack
		3.7 \AA~apart. (R-double) Monomers arrange vertically in a 2\textsubscript{1}
		helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots) Monomer
		tails are tilted with respect to the membrane plane. (R-pores) As derived from
		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally (b) (Reproduced
		from \citenum{feng_thin_2016}) The repeat spacing in the 1D small angle X-ray
		scattering pattern is characteristic of hexagonal packing. The leading peak,
		q*, represents the distance between the d\textsubscript{100} planes. Using this
		distance, we know that the distance between pore centers is 4.12 nm.} 
	\label{fig:SWAXS}
 \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
  \includegraphics[width=\linewidth]{monomer_diagonal.png}
  \caption{}
  \end{subfigure}
  \begin{subfigure}[t]{0.42\textwidth}
  \includegraphics[width=\linewidth]{stacked_monomers.png}
  \caption{}
  \end{subfigure}
  \begin{subfigure}[t]{0.35\textwidth}
  \includegraphics[width=\linewidth]{initial_pore.png}
  \caption{}
  \end{subfigure}
  \begin{subfigure}[t]{0.45\textwidth}
  \includegraphics[width=\linewidth]{initial_unit_cell.png}
  \caption{}
  \end{subfigure}
  \caption{(a) We parameterized a single monomer and annealed it to produce a low energy
		configuration. (b) We assembled monomers into columns by stacking them on top of each 
		other. (c) We duplicated each column and rotated them to create hydrophilic pore centers.
		We chose to stack twenty monomers into each column. (d) We duplicated the pores and 
		placed them into a monoclinic unit cell with hexagonal symmetry.}\label{fig:build_procedure}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{ralkanes.png}
  \caption{R-alkanes}\label{fig:ralkanes}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{rpi_rdouble.png}
  \caption{$q_z|_{r=0}$}\label{fig:rpi_rdouble}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{angular_integration.png}
  \caption{R-spots}\label{fig:rspots}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{saxs_xsection.png}
  \caption{R-pores}\label{fig:saxs_xsection}
  \end{subfigure}
  \caption{(a) We measured the intensity of R-alkanes by calculating the average 
  intensity within the region bounded by $|\mathbf{q}|$ = 1.4~$\AA^{-1}$ and 
  1.57~$\AA^{-1}$ (between 4.0 and 4.5 \AA~in real space). We excluded intensities
  within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$, since the 
  simulated spectra overlap with R-$\pi$ in those regions in all cases. (b) We
  measured the intensity of R-$\pi$ and R-double based on the peaks of the $q_z$
  cross-section of the diffraction pattern. (c) We measured the intensity of R-spots
  by averaging the peak heights produced by radially integrating the patterns within 
  the R-alkanes region. We took the intensity of R-spots as the average of the 
  peak intensities near -37 and -143$\degree$. (d) We measured the intensity of 
  R-pores by measuring the height of the d\textsubscript{100} peak (the leading
  peak closest to $q_r$=0) of the cross-section of the diffraction patterns along
  the $q_r$ axis at $q_z$=0.} \label{fig:xrd_intensities}
  %MRS13: it's confusing to have the same label (R-spots) beneath c and d.  Should be different labels if different data.
  \end{figure}

@@

  \begin{figure}[!htb]
	\centering
	\includegraphics[width=\linewidth]{p2p.png}
	\caption{Systems with 5 columns per pore have equilibrated pore spacings closest to
			 the experimental value of 4.12 nm. The equilibrated pore spacing of the model 	
			 increases as the number of columns in each pore increases.}~\label{fig:p2p}
  \end{figure}

@@

  \begin{figure}[!htb]
	\centering
	\begin{subfigure}{0.88\textwidth}
	\begin{subfigure}{0.28\linewidth}
			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_layered_300K_jet_nocbar.png}
			\end{subfigure}
			\begin{subfigure}{\textwidth}
		       		\centering
	        		\includegraphics[width=\linewidth]{rzplot_layered_300K_disorder_jet_nocbar.png}
			\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
	\centering
			\begin{subfigure}{\textwidth}
		       		\centering
	        		\includegraphics[width=\linewidth]{WAXS_raw_jet_nocbar.png}
			\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.28\linewidth}
	\centering
			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_offset_300K_jet_nocbar.png}
			\end{subfigure}

			\begin{subfigure}{\textwidth}
				\centering
			    \includegraphics[width=\linewidth]{rzplot_offset_300K_disorder_jet_nocbar.png}
			\end{subfigure}
	\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.1\textwidth}
		\centering
		\includegraphics[width=\linewidth]{colorbar_jet.png}
	\end{subfigure}	
	\caption{Simulated XRD patterns show some qualitative agreement with
		experiment. Shown is a comparison of the (a) Sandwiched, ordered basin (b)
		Sandwiched, disordered basin (d) Parallel displaced, ordered basin and (e)
		Parallel displaced, disordered basin configurations with (c) experimental WAXS.
		The major reflections of interest (See Figure~\ref{fig:SWAXS} for their
		definitions) are present at varying degrees. In all cases, R-pores, R-alkanes
		and R-$\pi$ are present to some degree. R-spots is also present, however it is
		generally partially covered by the broad R-$\pi$ reflection. Quantitative
		comparisons of the relative intensities and locations of reflections of
		interest are presented in Table~\ref{table:relative_intensities_300K}. In both
		XRD patterns generated from parallel displaced patterns, there is a faint line
		across $q_z \sim 0.7~$\AA$^{-1}$, half the simulated value of R-$\pi$. Although
		it does not cross through $q_r = 0$~\AA$^{-1}$, it is at the same $q_z$ value
		where we expect R-double to be present. Still, R-double is not fully reproduced
		in any of the simulated patterns.}~\label{fig:XRDsim} 
  \end{figure}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_rsection_fit.png}
  \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_rsection_fit.png}
  \caption{FWHM = 0.796 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_zsection_fit.png}
  \caption{FWHM = 0.110 $\pm$ 0.003 $\AA^{-1}$}\label{fig:exp_zsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_zsection_fit.png}
  \caption{FWHM = 0.163 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_zsection_fit}
  \end{subfigure}
  \caption{
  The maximum intensity of R-$\pi$ generated from simulations of the ordered
  parallel displaced configuration is 3 times larger than experiment. The $q_r$
  cross-section of R-$\pi$ ((a) and (b)) is qualitatively different between 
  experiment (a) and simulation (b). We fit Lorentzian profiles to each peak and
  the FWHM (full width at half maximum) of the simulated pattern agrees with experiment within error. However
  the fit to the simulated data is affected by the three sharp peaks which appear
  near $q_r$ = 0. The $q_z$ cross-sections of R-$\pi$ ((c) and (d)) are 
  qualitatively similar. Each fits a Lorentzian profile well, however the FWHM
  of the simulated cross-section (d) is 48\% larger than the experimental 
  cross-section. Additionally, the peak of the simulated $q_z$ cross-section is 
  located at a lower $q_z$ value than experiment.}\label{fig:rpi_exp_comparison}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_stds.png}
  \caption{}\label{fig:offset_ensemble_stds}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_means.png}
  \caption{}\label{fig:offset_ensemble_means}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_regional_density.png}
  \caption{}\label{fig:offset_ensemble_regional_density}
  \end{subfigure}
  \caption{(a) The standard deviation of the distribution of quenched disorder
  from the first 5 ns of the main ordered parallel displaced system studied in
  this paper (black dashed line) is in agreement with the distribution of quenched disorder 
  standard deviations calculated from the ensemble of simulations (histogram). 
  (b) The mean values of $r$ and $\theta$ from the first 5 ns of the main
  system trajectory (black dashed line) is in agreement with the distribution of mean values
  calculated from each simulation in the ensemble (histogram). The mean values of $z$
  are necessarily 0 so they are not plotted. (c) The radial densities of tail
  atoms, head group atoms and sodium atoms calculated from the first 5 ns of the
  main system simulation trajectory (black lines) and from the ensemble of 
  trajectories (all other lines) look qualitatively similar.}\label{fig:ensemble_stds}
  \end{figure}

>>>>

%MRS5: could be punchier. I will keep thinking.  
\title{Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes}
\author{Benjamin J. Coscia}
\author{Joe Yelk}
\author{Matthew A. Glaser}
\affiliation{Department of Physics, University of Colorado Boulder, Boulder CO, 80309, USA}
%\author{Richard D. Noble}
\author{Douglas L. Gin}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\alsoaffiliation{Department of Chemistry and Biochemistry, University of Colorado Boulder, Boulder CO 80309, USA}
\author{Xunda Feng}
\affiliation{Department of Chemical and Environmental Engineering, Yale University, New Haven, Connecticut 06511, USA}
\author{Michael R. Shirts}
\email{michael.shirts@colorado.edu}
\affiliation{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\begin{document}
%MRS13: we might end up adjusting the author list a bit; I will ask Matt where he thinks he and Joe should go.  I will talk to Rich when we get this going; not clear that he actually has contributed.  But that's my job. 
  \graphicspath{{./figures/}}

@@

  \begin{figure}
	\centering
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{NaGA3C11.eps}
		\caption{}~\label{fig:monomer}
	\end{subfigure}
	\begin{subfigure}{.3\textwidth}
		\centering
		\includegraphics[width=\textwidth]{monomer_twocolor.pdf}
		\caption{}~\label{fig:atomistic_monomer}
	\end{subfigure}
	\begin{subfigure}{0.3\linewidth}
		\centering
		\includegraphics[width=\textwidth]{wedge_thick.pdf}
		\caption{}~\label{fig:wedge}
	\end{subfigure}
		\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{columns.pdf}
		\caption{}~\label{fig:wedge_layer}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
		\centering
		\includegraphics[width=\textwidth]{hexagonal_packing.pdf}
		\caption{}~\label{fig:hex_packing_simple}
	\end{subfigure}
	\caption{(a) The LLC monomer Na-GA3C11 (b) rendered atomistically (c)
	exhibits wedge-like character. (d) Monomers stack on top of each other to
	create columns with short range order then assemble into pores with  
	hydrophilic head groups (blue) face towards the pore center. (e) The 
	pores assemble into hexagonally packed columnar mesophases.}~\label{fig:assembly}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{cartoon_pore.pdf}
		\caption{}~\label{fig:undetailed_pore}
	\end{subfigure}
	\begin{subfigure}{0.45\linewidth}
		\centering
		\includegraphics[width=\textwidth]{detailed_pore.pdf}
		\caption{}~\label{fig:detailed_pore}
	\end{subfigure}
    \caption{(a) Previous understanding of the pores are essentially speculations 
    based on limited chemical and experimental data. (b) We use detailed molecular 
    modeling in this paper in order to appropriately model the pore's complex architecture
    which is crucial to understanding the mechanism of solute transport. In both 
    pictures, the head group region is colored blue and the tail region is colored cyan.}~\label{fig:detail}
  \end{figure}

@@

  \begin{figure}[!htb]
        \centering
                \begin{subfigure}[t]{0.495\linewidth}
                \centering
                \includegraphics[width=\linewidth]{WAXS_annotated_words.pdf} 
                \caption{}\label{fig:WAXS}
        \end{subfigure}
	\begin{subfigure}[t]{0.405\linewidth}
                \centering
                \includegraphics[width=\textwidth]{SAXS.pdf}
                \caption{}\label{fig:SAXS}
        \end{subfigure}
	\caption{(a) 2D WAXS gives details about repeating features on the
		order of angstroms. Experimentalists have explained each of the 5 major
		reflections present as follows: (R-$\pi$) Aromatic head groups $\pi-\pi$ stack
		3.7 \AA~apart. (R-double) Monomers arrange vertically in a 2\textsubscript{1}
		helix. (R-alkanes) Alkane chain tails pack 4.5 \AA~apart. (R-spots) Monomer
		tails are tilted with respect to the membrane plane. (R-pores) As derived from
		SAXS, the pores are spaced 4.12 nm apart and pack hexagonally (b) (Reproduced
		from \citenum{feng_thin_2016}) The repeat spacing in the 1D small angle X-ray
		scattering pattern is characteristic of hexagonal packing. The leading peak,
		q*, represents the distance between the d\textsubscript{100} planes. Using this
		distance, we know that the distance between pore centers is 4.12 nm.} 
	\label{fig:SWAXS}
 \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}[t]{0.45\textwidth}
  \includegraphics[width=\linewidth]{monomer_diagonal.pdf}
  \caption{}
  \end{subfigure}
  \begin{subfigure}[t]{0.42\textwidth}
  \includegraphics[width=\linewidth]{stacked_monomers.pdf}
  \caption{}
  \end{subfigure}
  \begin{subfigure}[t]{0.35\textwidth}
  \includegraphics[width=\linewidth]{initial_pore.pdf}
  \caption{}
  \end{subfigure}
  \begin{subfigure}[t]{0.45\textwidth}
  \includegraphics[width=\linewidth]{initial_unit_cell.pdf}
  \caption{}
  \end{subfigure}
  \caption{(a) We parameterized a single monomer and annealed it to produce a low energy
		configuration. (b) We assembled monomers into columns by stacking them on top of each 
		other. (c) We duplicated each column and rotated them to create hydrophilic pore centers.
		We chose to stack twenty monomers into each column. (d) We duplicated the pores and 
		placed them into a monoclinic unit cell with hexagonal symmetry.}\label{fig:build_procedure}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{ralkanes.pdf}  % Search WAXS.py for: fancy demo of r-alkanes normalization
  \caption{R-alkanes}\label{fig:ralkanes}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{rpi_rdouble.pdf}  %  Search WAXS.py for: R-pi / R-double intensity measurement illustration
  \caption{$q_z|_{r=0}$}\label{fig:rpi_rdouble}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{angular_integration.pdf} % Search WAXS.py for: Plot R-spots integrated intensity curve
  \caption{R-spots}\label{fig:rspots}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{saxs_xsection.pdf}  % 2DSAXS.py in Scripts folder 
  \caption{R-pores}\label{fig:saxs_xsection}
  \end{subfigure}
  \caption{(a) We measured the intensity of R-alkanes by calculating the average 
  intensity within the region bounded by $|\mathbf{q}|$ = 1.4~$\AA^{-1}$ and 
  1.57~$\AA^{-1}$ (between 4.0 and 4.5 \AA~in real space). We excluded intensities
  within $\pm$ 30\degree~of the meridional axis defined by $q_r=0$, since the 
  simulated spectra overlap with R-$\pi$ in those regions in all cases. (b) We
  measured the intensity of R-$\pi$ and R-double based on the peaks of the $q_z$
  cross-section of the diffraction pattern. (c) We measured the intensity of R-spots
  by averaging the peak heights produced by radially integrating the patterns within 
  the R-alkanes region. We took the intensity of R-spots as the average of the 
  peak intensities near -37 and -143$\degree$. (d) We measured the intensity of 
  R-pores by measuring the height of the d\textsubscript{100} peak (the leading
  peak closest to $q_r$=0) of the cross-section of the diffraction patterns along
  the $q_r$ axis at $q_z$=0.} \label{fig:xrd_intensities}
  %MRS13: it's confusing to have the same label (R-spots) beneath c and d.  Should be different labels if different data.
  \end{figure}

@@

  \begin{figure}[!htb]
	\centering
	\includegraphics[width=\linewidth]{p2p.pdf}
	\caption{Systems with 5 columns per pore have equilibrated pore spacings closest to
			 the experimental value of 4.12 nm. The equilibrated pore spacing of the model 	
			 increases as the number of columns in each pore increases.}~\label{fig:p2p}
  \end{figure}

@@

  \begin{figure}[!htb]
	\centering
	\begin{subfigure}{0.88\textwidth}
	\begin{subfigure}{0.28\linewidth}
			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_layered_300K_jet_nocbar.pdf}
			\end{subfigure}
			\begin{subfigure}{\textwidth}
		       		\centering
	        		\includegraphics[width=\linewidth]{rzplot_layered_300K_disorder_jet_nocbar.pdf}
			\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.4\linewidth}
	\centering
			\begin{subfigure}{\textwidth}
		       		\centering
	        		\includegraphics[width=\linewidth]{WAXS_raw_jet_nocbar.pdf}
			\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.28\linewidth}
	\centering
			\begin{subfigure}{\textwidth}
			\centering
		        	\includegraphics[width=\linewidth]{rzplot_offset_300K_jet_nocbar.pdf}
			\end{subfigure}

			\begin{subfigure}{\textwidth}
				\centering
			    \includegraphics[width=\linewidth]{rzplot_offset_300K_disorder_jet_nocbar.pdf}
			\end{subfigure}
	\end{subfigure}
	\end{subfigure}
	\begin{subfigure}{0.1\textwidth}
		\centering
		\includegraphics[width=\linewidth]{colorbar_jet.pdf}
	\end{subfigure}	
	\caption{Simulated XRD patterns show some qualitative agreement with
		experiment. Shown is a comparison of the (a) Sandwiched, ordered basin (b)
		Sandwiched, disordered basin (d) Parallel displaced, ordered basin and (e)
		Parallel displaced, disordered basin configurations with (c) experimental WAXS.
		The major reflections of interest (See Figure~\ref{fig:SWAXS} for their
		definitions) are present at varying degrees. In all cases, R-pores, R-alkanes
		and R-$\pi$ are present to some degree. R-spots is also present, however it is
		generally partially covered by the broad R-$\pi$ reflection. Quantitative
		comparisons of the relative intensities and locations of reflections of
		interest are presented in Table~\ref{table:relative_intensities_300K}. In both
		XRD patterns generated from parallel displaced patterns, there is a faint line
		across $q_z \sim 0.7~$\AA$^{-1}$, half the simulated value of R-$\pi$. Although
		it does not cross through $q_r = 0$~\AA$^{-1}$, it is at the same $q_z$ value
		where we expect R-double to be present. Still, R-double is not fully reproduced
		in any of the simulated patterns.}~\label{fig:XRDsim} 
  \end{figure}

@@

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_rsection_fit.pdf}
  \caption{FWHM = 0.792 $\pm$ 0.009 $\AA^{-1}$}\label{fig:exp_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_rsection_fit.png}
  \caption{FWHM = 0.796 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_rsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{exp_zsection_fit.pdf}
  \caption{FWHM = 0.110 $\pm$ 0.003 $\AA^{-1}$}\label{fig:exp_zsection_fit}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{sim_zsection_fit.png}
  \caption{FWHM = 0.163 $\pm$ 0.011 $\AA^{-1}$}\label{fig:sim_zsection_fit}
  \end{subfigure}
  \caption{
  The maximum intensity of R-$\pi$ generated from simulations of the ordered
  parallel displaced configuration is 3 times larger than experiment. The $q_r$
  cross-section of R-$\pi$ ((a) and (b)) is qualitatively different between 
  experiment (a) and simulation (b). We fit Lorentzian profiles to each peak and
  the FWHM (full width at half maximum) of the simulated pattern agrees with experiment within error. However
  the fit to the simulated data is affected by the three sharp peaks which appear
  near $q_r$ = 0. The $q_z$ cross-sections of R-$\pi$ ((c) and (d)) are 
  qualitatively similar. Each fits a Lorentzian profile well, however the FWHM
  of the simulated cross-section (d) is 48\% larger than the experimental 
  cross-section. Additionally, the peak of the simulated $q_z$ cross-section is 
  located at a lower $q_z$ value than experiment.}\label{fig:rpi_exp_comparison}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_stds.png}
  \caption{}\label{fig:offset_ensemble_stds}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_means.png}
  \caption{}\label{fig:offset_ensemble_means}
  \end{subfigure}
  \begin{subfigure}{\textwidth}
  \includegraphics[width=\textwidth]{offset_ensemble_regional_density.pdf}
  \caption{}\label{fig:offset_ensemble_regional_density}
  \end{subfigure}
  \caption{(a) The standard deviation of the distribution of quenched disorder
  from the first 5 ns of the main ordered parallel displaced system studied in
  this paper (black dashed line) is in agreement with the distribution of quenched disorder 
  standard deviations calculated from the ensemble of simulations (histogram). 
  (b) The mean values of $r$ and $\theta$ from the first 5 ns of the main
  system trajectory (black dashed line) is in agreement with the distribution of mean values
  calculated from each simulation in the ensemble (histogram). The mean values of $z$
  are necessarily 0 so they are not plotted. (c) The radial densities of tail
  atoms, head group atoms and sodium atoms calculated from the first 5 ns of the
  main system simulation trajectory (black lines) and from the ensemble of 
  trajectories (all other lines) look qualitatively similar.}\label{fig:ensemble_stds}
  \end{figure}
